\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage{url}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\topmargin=0in
\topskip=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}
  {\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}
  {\end{list}}

  
  
\begin{document}
\name{\LARGE Aaron Craig's CV}
\begin{resume}

  \section{\sc Contact Info}
    \vspace{.05in}
    \begin{tabular}{@{}p{3.5in}p{3in}}
      {Email}: aaroncraig@protonmail.ch & 20D Portland Crescent \\
      {Website}:  \url{github.com/craigthelinguist}& Thorndon, Wellington \\
    \end{tabular}

   \section{\sc Skills}
    {\bf Programming Languages}: Java, C, Python, Prolog, Haskell, SQL\\
    {\bf Modelling Languages}: Alloy, UML, LTSA, Isabelle\\
    {\bf Markup Languages}: Latex, Markdown, JSON, XML\\
    {\bf Libraries \& Frameworks}: JUnit, pandas, matplotlib, numpy, curses, OpenGL, XStream, Berkeley Socket API, Swing, Unity\\
    {\bf Protocols}: HTTP, DNS

  \section{\sc Job History}
  
  	{\bf Victoria University}, Wellington\\
  	{\em Research Assistant} \hfill {Oct 2015 -- Current}
  	\begin{list2}
  		\item Contributed to the Wyvern interpreter: \url{github.com/wyvernlang/wyvern}
		\item Developed a type system for effect inference in record calculi.
  		\item My supervisors are \href{http://homepages.mcs.vuw.ac.nz/~alex/}{\textit{Alex Potanin}} and \href{http://www.cs.cmu.edu/~./aldrich/index.html}{\textit{Jonathan Aldrich}}.
	\end{list2}
  
    {\bf New Zealand Registry Services}, Wellington\\
    {\em Research Intern} \hfill {Oct 2014 -- Current}
    \begin{list2}
	\item Analysis and summary of DNS data with pandas, matplotlib.
	\item Detection and classification of botnet domains using clustering techniques.
	\item Gather, verify, analyse routing data for generating maps of NZ internet.
	\item Natural language processing on domain names.
    \end{list2}

    {\bf Victoria University}, Wellington\\
    {\em Sessional Assistant \& Tutor} \hfill {Mar 2014 -- Oct 2015}
    \begin{list2}
	\item Marking tests and assignments; invigilating.
	\item Running tutorials, labs, and helpdesks.
	\item Classes tutored: Intro to Computer Science; Engineering Modelling \& Design; Data Structures \& Algorithms II; Formal Foundations of Programming.
    \end{list2}

  {\bf Converga Ltd.}, Petone\\
  {\em Business Processing Clerk} \hfill {Nov 2013 -- Mar 2014}
  \begin{list2} %Job Description%
	\item Data entry and verification.
	\item Sorting files by hand. (I did this using radix sort)
  \end{list2}

  {\bf Target Furniture}, Porirua\\
  {\em Temp, Storeperson} \hfill{Nov 2010 -- May 2013}
  \begin{list2} %Job Description%
	\item Furniture removal, delivery, assembly, and repair. 
	\item Managing inventory, driving forklift.
	\item Training temps.
	\item Greeting and assisting customers.
  \end{list2}

%%%%%%%%%%%
%%%%%%%%%%%%%%%%

\section{\sc Interests \& Projects}

{\bf Natural Language Processing}. One of my dreams is to develop and improve algorithms for recognising and producing human language. I have made several corpora for M\=aori and NZ English. At NZRS I looked at detecting botnet activity in DNS by classifying domain names. As part of that I gave a presentation at the 2015 NZ Internet Research Forum.

{\bf Programming Languages}. Exploring the space of formal languages helps shed light on the mysteries of natural languages. Furthermore, the role of language in software development is critically underappreciated. I want to develop expressive, safe ways for programmers to write software. I'm a contributor to the Wyvern project and especially interested in type systems and static analysis.

{\bf Visualisations.} At NZRS I helped verify data used to generate a map of the NZ internet. I've written several interactive visualisations for algorithms (A*, Kruskal's Knight's Tour, KNN), cellular automata, and Turing machines. These are all much easier to explain in pictures than in words or mathematical formalism, which can be cumbersome and unintuitive.

{\bf Education.} I would like to see NZ education offer more in the way of computer science and logic for high school students and would be excited to work towards such goals. I like the idea of using history-themed games to convey the geopolitics of an era.

{\bf Game Development}. Each year I attend Pixeljam, a 48hr gamejam in Wellington. Over the years we've made several flavours of game such as: a lane-runner, a Mario-style platformer, and a 3d horror game.

\section{\sc Education}
{\bf Victoria University of Wellington}, New Zealand
\begin{list2}
	\item STAR Programme \hfill 2011
	\item BA Linguistics \& Philosophy \hfill 2012
	\item BSc Computer Science \& Mathematics \hfill 2013 -- Current
	\item BSc Hons. Computer Science \hfill 2016 -- Current
\end{list2}

{\bf Tawa College}, New Zealand
\begin{list2}
	\item NCEA Level 3 (Merit endorsement) \hfill 2011
\end{list2}

\section{\sc Scholarships \& Awards}

{\bf Victoria University of Wellington}
\begin{list2}
	\item Victoria Achievers Scholarship \hfill 2012
	\item Dean's List \hfill Current
\end{list2}

{\bf Tawa College}
\begin{list2}
	\item Katherine Mansfield Award (English) \hfill 2011
	\item Leanne Dixon Cup (History) \hfill 2011
	\item NZQA Outstanding English Scholarship \hfill 2011
\end{list2}

\section{\sc Languages}
English\\
M\=aori (Elementary)

\section{\sc About Me}
I was born in Porirua and live in Wellington. I like creative writing and reading history, philosophy, and fiction. For two years I boxed as an amateur but nowadays just like to watch. My tribe is Mua\=upoko, in Horowhenua.

\section{\sc References}
Available upon request.

\end{resume}
\end{document}




