%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{purple}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean


\newcommand\Colorhref[3][blue]{\href{#2}{\small\color{#1}#3}}


% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{}{Aaron Craig}
\title{CV}                               % optional, remove / comment the line if not wanted
\address{36 Tongariro Drive, Porirua, New Zealand}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{027 755 2760}                   % optional, remove / comment the line if not wanted
% \phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
% \phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{aaroncraig@protonmail.ch}                               % optional, remove / comment the line if not wanted
% \homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
\extrainfo{Github: \Colorhref{https://github.com/craigthelinguist}{https://github.com/craigthelinguist}}
% \extrainfo{additional information}                 % optional, remove / comment the line if not wanted
% \photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
% \quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Languages}
\cvitem{Proficient}{C, Java, Prolog, Python, Rust}
\cvitem{Familiarity}{Bash, C++, Haskell, Isabelle, \LaTeX, SPARK Ada, SQL}

\section{Frameworks, Tools, Libraries, Platforms, Protocols}
Alloy, Berkeley Sockets, Cargo, cjson, curses, DNS, Git, GNU Make, HTTP, JSON, JUnit, Linux, LTSA, matplotlib, nltk, numpy, pandas, SDL2, Swing, Unity, XML, XStream

\section{Experience}
\cventry{2017}{Intern}{Oracle Labs}{Brisbane, Australia}{}{Worked in the secure languages group to investigate the feasibility and limitations of languages such as Rust in secure software development.
\begin{itemize}%
\item Ported from C to Rust \Colorhref{https://github.com/oracle/NVM-Direct}{a library} for open-nested transactions in non-volatile memory.
\end{itemize}}

\cventry{2015-2017}{Research Assistant}{Victoria University of Wellington}{}{}{Worked on the compiler and effect system of \Colorhref{http://www.cs.cmu.edu/~aldrich/wyvern/}{Wyvern}.
\begin{itemize}
\item Implemented Wyvern intermediate language semantics and dynamic typing
\item Added and updated integration tests for module system (JUnit).
\item Developed a lightweight capability-based effect system and proved it sound.
\end{itemize}}

\cventry{2014-2017}{Tutor}{Victoria University of Wellington}{}{}{Marking tests and assignments; invigilating; running tutorials, labs, lectures, and helpdesks.
\begin{itemize}
\item Intro to Computer Science (2014)
\item Engineering Modelling \& Design (2014)
\item Data Structures \& Algorithms II (2015)
\item Formal Foundations of Programming (2015)
\item Programming Languages (2016)
\item Data Structures \& Algorithms II (2017)
\end{itemize}}

\cventry{2014-2016}{Research Intern}{New Zealand Registry Services}{Wellington}{}{Data analysis and visualisation of New Zealand's DNS traffic.
\begin{itemize}
\item Data analysis on a Hadoop cluster using Python, pandas, numpy, matplotlib, and SQL.
\item Analysis of routing data in Python. This was used to generate a \Colorhref{http://bgp.topology.net.nz/}{BGP topology map}.
\item Anomaly and botnet detection on domain names using clustering techniques and natural language processing (nltk, Python).
\end{itemize}}

\cventry{2013-2014}{Business Processing Clerk}{Converga Ltd.}{Petone}{}{Data entry, verification, sorting files.}

\cventry{2010-2013}{Storeman}{Target Furniture}{Porirua}{}{Furniture removal, delivery, assembly, and repair; managing inventory; driving forklift.}

\section{Personal Projects}

\cvitem{\Colorhref{https://www.github.com/craigthelinguist/automata}{automata}}{A visualisation of cellular automata in C with curses.}

\cvitem{\Colorhref{https://github.com/craigthelinguist/fsms}{fsms}}{The Miller-Rabin powerset construction in Prolog, which proves non-deterministic state machines and deterministic state machines are computationally equivalent.}

\cvitem{\Colorhref{https://github.com/craigthelinguist/minifx}{minifx}}{A Java interpreter for an effect-conscious LISP dialect.}

\cvitem{pxljam}{pxljam is a game jam event in Wellington. Over the years I've made several kinds of games, such as a \Colorhref{https://github.com/haiquangtran/Sugoi-Tran}{platformer} (Java, Swing), a \Colorhref{https://github.com/OliverGreenaway/YOLO}{lane-runner} (Java, Swing), and a \Colorhref{https://github.com/EwanMoshi/FruitSeller}{3D horror game} (Unity, C\#).}

\cvitem{\Colorhref{https://github.com/mreiland/trustiNES}{trustines}}{A collaborative project to build an emulator for the NES (and 6502 microprocessor).}

\section{Publications \& Talks}

\textit{\Colorhref{http://homepages.mcs.vuw.ac.nz/~alex/files/CraigPotaninGrovesAldrichOCAP2017.pdf}{Capability-Based Effects}}. Aaron Craig, Lindsay Groves, Alex Potanin, Jonathan Aldrich. OCAP Workshop, SPLASH, Vancouver, 2017.\\

\textit{Jumping Into a Pool of Data}. Aaron Craig. New Zealand Internet Research Forum, Auckland, New Zealand, 2015.

\section{Education}
\cventry{2017}{B.Sc. Hons. Computer Science}{Victoria University of Wellington}{}{}{Thesis: \Colorhref{https://github.com/wyvernlang/docs/blob/master/design/effects/honours/thes.pdf}{Capability-Flavoured Effects} \\ Supervisors: Alex Potanin, Jonathan Aldrich (Carnegie Mellon), Lindsay Groves}
\cventry{2016}{B.Sc. Computer Science \& Mathematics}{Victoria University of Wellington}{}{}{}
\cventry{2011}{Tawa College}{Tawa, Wellington}{}{}{ NZQA Outstanding English Scholarship \\ NCEA Level 3 (Merit Endorsement)}

\section{Volunteering}
\cventry{2016-2017}{Volunteer}{Samaritans}{Wellington}{}{Providing emotional comfort and support to callers at the 24-hour crisis hotline.}

\section{Personal}
\cvitem{Interests}{Type/effect systems, logic, computability theory, programming languages, capabilities}
\cvitem{Hobbies}{Reading, writing, guitar, boxing, history, videogames}
\cvitem{Languages}{English (fluent), M\=aori (elementary)}

\section{References}
Available upon request.


\end{document}


%% end of file `template.tex'.
