\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage{url}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\topmargin=0in
\topskip=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}
  {\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}
  {\end{list}}

  
  
\begin{document}
\name{\LARGE Aaron Craig's CV}
\begin{resume}

  \section{\sc Contact Info}
    \vspace{.05in}
    \begin{tabular}{@{}p{3.5in}p{3in}}
      {Email}: aaroncraig@protonmail.ch & Unit 15, 33-35 Jellicoe St\\
      {Website}:  \url{github.com/craigthelinguist}& Loganlea, Brisbane, Australia \\
    \end{tabular}

   \section{\sc Skills}
    {\bf Programming Languages}: Java, C, Rust, Python, Prolog, Haskell, SQL\\
    {\bf Modelling Languages}: Alloy, UML, LTSA, Isabelle\\
    {\bf Other Languages}: Latex, Markdown, JSON, XML\\
    {\bf Libraries \& Frameworks}: JUnit, pandas, matplotlib, numpy, curses, OpenGL, XStream, Berkeley Socket API, Swing, Unity\\
    {\bf Protocols}: HTTP, DNS

  \section{\sc Job History}

    	{\bf Oracle Labs}, Brisbane, Australia\\
  	{\em Research Intern} \hfill {July 2017 -- Current}
  	\begin{list2}
  		\item Work in secure programming languages group to investigate safe systems programming languages.
		\item Ported the nvm-direct library to Rust.
	\end{list2}

  	{\bf Victoria University}, Wellington, NZ\\
  	{\em Research Assistant} \hfill {Oct 2015 -- Current}
  	\begin{list2}
  		\item Contributed to the Wyvern interpreter: \url{github.com/wyvernlang/wyvern}
		\item Worked on effect inference in capability-safe languages.
  		\item My supervisors are \href{http://homepages.mcs.vuw.ac.nz/~alex/}{\textit{Alex Potanin}} and \href{http://www.cs.cmu.edu/~./aldrich/index.html}{\textit{Jonathan Aldrich}}.
	\end{list2}
  
    {\bf New Zealand Registry Services}, Wellington, NZ\\
    {\em Research Intern} \hfill {Oct 2014 -- Current}
    \begin{list2}
	\item Analysis and summary of DNS data with pandas, matplotlib.
	\item Detection and classification of botnet domains using clustering techniques.
	\item Gather, verify, analyse routing data for generating maps of NZ internet.
	\item Natural language processing on domain names.
    \end{list2}

    {\bf Victoria University}, Wellington, NZ\\
    {\em Sessional Assistant \& Tutor} \hfill {Mar 2014 -- Jul 2017}
    \begin{list2}
	\item Marking tests and assignments; invigilating.
	\item Running tutorials, labs, lectures, and helpdesks.
	\item Classes tutored: Intro to Computer Science (2014); Engineering Modelling \& Design (2014); Data Structures \& Algorithms II (2015); Formal Foundations of Programming (2015); Programming Languages (2016); Data Structures \& Algorithms II (2017)
    \end{list2}

  {\bf Converga Ltd.}, Petone, NZ\\
  {\em Business Processing Clerk} \hfill {Nov 2013 -- Mar 2014}
  \begin{list2} %Job Description%
	\item Data entry and verification.
	\item Sorting files by hand. (I did this using radix sort)
  \end{list2}

  {\bf Target Furniture}, Porirua, NZ\\
  {\em Temp, Storeperson} \hfill{Nov 2010 -- May 2013}
  \begin{list2} %Job Description%
	\item Furniture removal, delivery, assembly, and repair. 
	\item Managing inventory, driving forklift.
	\item Training temps.
	\item Greeting and assisting customers.
  \end{list2}

%%%%%%%%%%%
%%%%%%%%%%%%%%%%



\section{\sc Presentations}
Aaron Craig. {\it Jumping Into a Pool of Data}. NZ Internet Research Forum 2015.


Aaron Craig, Lindsay Groves, Alex Potanin, Jonathan Aldrich. {\it Capability-Flavoured Effects}. OCAP Workshop, SPLASH, 2017.

\section{\sc Education}
{\bf Victoria University of Wellington}, New Zealand
\begin{list2}
	\item STAR Programme \hfill 2011
	\item BSc Computer Science \& Mathematics \hfill 2016
	\item BSc Hons. Computer Science \hfill 2017
\end{list2}

{\bf Tawa College}, New Zealand
\begin{list2}
	\item NCEA Level 3 (Merit endorsement) \hfill 2011
\end{list2}

\section{\sc Scholarships \& Awards}

{\bf Victoria University of Wellington}
\begin{list2}
	\item Victoria Achievers Scholarship \hfill 2012
	\item Dean's List \hfill Current
\end{list2}

{\bf Tawa College}
\begin{list2}
	\item Katherine Mansfield Award (English) \hfill 2011
	\item Leanne Dixon Cup (History) \hfill 2011
	\item NZQA Outstanding English Scholarship \hfill 2011
\end{list2}


\section{\sc Interests} Type systems, effect systems, object capabilities, compiler engineering, computability, decidability, formal methods, natural language processing, programming languages, modal logic


\section{\sc Languages}
English\\
M\=aori (Elementary)

\section{\sc About Me}
I was born in Porirua and live in Wellington. I like creative writing and reading history, philosophy, and fiction. For two years I boxed as an amateur but nowadays just like to watch. My tribe is Mua\=upoko, in Horowhenua.

\section{\sc References}
Available upon request.

\end{resume}
\end{document}




